---
title: "SHARE OF VOICE REPORT"
author: "Croatian social media overview for October, 2021"
date: ""
# subtitle: "<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>"
subtitle: "Xiaomi"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts] 
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(knitr)
opts_chunk$set(
  fig.align="center", #fig.width=6, fig.height=4.5, 
  # out.width="748px", #out.length="520.75px",
  dpi=400, #fig.path='Figs/',
  cache=F#, echo=F, warning=F, message=F
  )


# Define pink color
red_pink <- "#e64173"
turquoise <- "#20B2AA"
orange <- "#FFA500"
red <- "#fb6107"
blue <- "#2b59c3"
green <- "#8bb174"
grey_light <- "grey70"
grey_mid <- "grey50"
grey_dark <- "grey20"
purple <- "#6A5ACD"
slate <- "#314f4f"
# Dark slate grey: #314f4f
# Knitr options

```

```{css, echo = F, eval = T}
@media print {
  .has-continuation {
    display: block !important;
  }
}
remark-slide-content {
  font-size: 22px;
  padding: 20px 80px 20px 80px;
}
.remark-code, .remark-inline-code {
  background: #f0f0f0;
}
.remark-code {
  font-size: 16px;
}
.mid. remark-code { /*Change made here*/
  font-size: 60% !important;
}
.tiny .remark-code { /*Change made here*/
  font-size: 40% !important;
}
```

```{r library, warning=F, echo=F, message=F, eval=TRUE}


library(tidyverse)  # data manipulation and visualization
library(gridExtra)  # plot arrangement
library(patchwork)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(tidyr)
library(janitor)
library(httr)
library(tidytext)
library(kableExtra)
library(data.table)
library(scales)
library(readxl)


```


# Contents

<br>
<br>



1. [Forums](#for)

---

class: inverse, center, middle
name: for

# FORUMS

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Important media for technology consumer market in Croatia.)

---


```{r importForums, echo=FALSE, message=FALSE, warning=FALSE}

rm(list=ls())

site_data_columns <- read_excel("../dta/10-21.xlsx",
                               sheet = "Forums")

site_data_column_names <- colnames(site_data_columns)
column_data_types <- c()
for(i in 1 : length(site_data_column_names)){  

    #where date is a column name
    if(site_data_column_names[i] == "date"){
         column_data_types[i] <- "date"

         #where result is a column name
         } else if (site_data_column_names[i] == "result") {
                      column_data_types[i] <- "numeric"

         } else{
                column_data_types[i] <- "text"
        }
}
column_data_types[5] <- "date"
column_data_types[10] <- "guess"



forums <- readxl::read_excel("../dta/10-21.xlsx",
                               sheet = "Forums",
                               col_types = column_data_types) %>% 
  row_to_names(.,1) %>% 
  clean_names() %>%
  select(title,text,"Date" = na,source,url, type, impressions, engagements, author) %>%
  mutate(impressions = as.numeric(impressions)) %>%
  mutate(engagements = as.numeric(engagements))


```

# Most important forums (activity)
<br>

```{r , echo=FALSE, message=FALSE, warning=FALSE}

forums %>%
  group_by(source) %>%
  count() %>%
  arrange(desc(n)) %>%
  rename("Forum" = source, "No. of occurences" = n)  %>% 
  kable() %>%
    kable_styling() %>%
    scroll_box(width = "750px", height = "400px")

```

.footnote[[*]Occurences denote the activity on a forum that mentions the brand.]

---

# Most important forums (impressions)
<br>
<br>

```{r, echo=FALSE, message=FALSE, warning=FALSE}

forums %>%
  group_by(source) %>%
  summarise(Impressions = sum(impressions, na.rm = TRUE)) %>%
  arrange(desc(Impressions)) %>% 
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
    scroll_box(width = "750px", height = "400px")
  
  
```

---

# Most important forums (engagements)
<br>
<br>

```{r, echo=FALSE, message=FALSE, warning=FALSE}

forums %>%
  group_by(source) %>%
  summarise(Engagements = sum(engagements, na.rm = TRUE)) %>%
  arrange(desc(Engagements)) %>% 
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
    scroll_box(width = "750px", height = "400px")
  
  
```


---

# Most important influencers
<br>
<br>


```{r, echo=FALSE, message=FALSE, warning=FALSE}

forums %>%
  group_by(author, source) %>%
  summarise(Impressions = sum(impressions, na.rm = TRUE),
            Activity = n()) %>%
  arrange(desc(Impressions)) %>%
  filter(Impressions > 400) %>% 
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
     scroll_box(width = "700px", height = "400px")
  
  
```





---

# CONTACT

<br>
<br>
<br>
<br>
**LUKOS**, obrt za informacijske djelatnosti
<br>
Novska, Vinogradska ulica 3G
<br>
doc.dr.sc.Luka Šikić
<br><br>
Kontakt:
<br>
mob: 098/162-30-52
<br>
email:lukos.usluge@gmail.com
<br>





























































