---
title: "SHARE OF VOICE REPORT"
author: "Croatian social media overview for July, 2021"
date: "Contentio d.o.o"
# subtitle: "<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>"
subtitle: "Xiaomi"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts] 
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(knitr)
opts_chunk$set(
  fig.align="center", #fig.width=6, fig.height=4.5, 
  # out.width="748px", #out.length="520.75px",
  dpi=300, #fig.path='Figs/',
  cache=F#, echo=F, warning=F, message=F
  )
```

```{css, echo = F, eval = T}
@media print {
  .has-continuation {
    display: block !important;
  }
}
remark-slide-content {
  font-size: 22px;
  padding: 20px 80px 20px 80px;
}
.remark-code, .remark-inline-code {
  background: #f0f0f0;
}
.remark-code {
  font-size: 16px;
}
.mid. remark-code { /*Change made here*/
  font-size: 60% !important;
}
.tiny .remark-code { /*Change made here*/
  font-size: 40% !important;
}
```

```{r paketi, warning=F, echo=F, message=F, eval=FALSE}

library(FactoMineR)
library(factoextra)
library(FactoMineR)
library(tidyverse)  # data manipulation and visualization
library(gridExtra)  # plot arrangement
library(patchwork)
library(ggplot2)
library(lavaan)
library(sem)
library(semPlot)
library(tidyverse)
library(dplyr)
library(polycor)
library(GPArotation)
```

# Contents

<br>
<br>
<br>


1. [General Overview](#gen)

2. [Facebook](#fb)

3. [Forums](#for)

4. [Portals](#port)

5. [Twitter](#tw)

6. [Youtube](#yt)

7. [Press](#pres)

8. [TV](#tv)


---
class: inverse, center, middle
name: gen

# GENERAL OVERVIEW

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Trends)

---

# Frequency of mention
<br>

 
 
<br>
<br>
.footnote[[*]Number of mentions in the whole text corpora.]
---

# Frequency of publication
<br>
<br>



.footnote[[*]Number of publications in the whole text corpora.]

---

# Media landscape frequency




---

class: inverse, center, middle
name: fb

# FACEBOOK

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Trends on the biggest Croatian social network)

---


# Most important publications
<br>
<br>


- add size of the channels

---

# Most important authors
<br>
<br>


---

class: inverse, center, middle
name: for

# FORUMS

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Very important media for mobile phone market in Croatia)

---


# Most important forums
<br>
<br>


- add size of the channels

---

# Activity description
<br>
<br>


---

# Most importan authors
<br>
<br>

---

class: inverse, center, middle
name: port

# PORTALS

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Usualy the original content to be shared across social media)

---


# Most important portals
<br>
<br>


- add size of the channels

---

# Number of publications 
<br>
<br>


---

# Content analysis

---

class: inverse, center, middle
name: tw

# TWITTER

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Informed minority in Croatia)

---


# Most important authors
<br>
<br>


- add size of the channels

---

# Authors by the audience size
<br>
<br>


---
# Number of publications
<br>
<br>


---

class: inverse, center, middle
name: yt

# YOUTUBE

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(People that wants to know details)

---

# Videos by type
<br>
<br>


---

# Most important videos 
<br>
<br>

- analyse impressons


---

# Most important authors
<br>
<br>



---

class: inverse, center, middle
name: pres

# PRESS

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Not very important)

---


# Most important sources
<br>
<br>


---

class: inverse, center, middle
name: tv

# TV

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Very rare)

---


# Most important sources
<br>
<br>

---

# CONTACT
<br>
<br>
### Contentio d.o.o
<br>
Adress:
<br>
Phone:
<br>
Mail:
<br>
Web:



































<br>
<br>







