---
title: "SHARE OF VOICE REPORT"
author: "Croatian social media overview for July, 2021"
date: "Contentio d.o.o"
# subtitle: "<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>"
subtitle: "Xiaomi"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts] 
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(knitr)
opts_chunk$set(
  fig.align="center", #fig.width=6, fig.height=4.5, 
  # out.width="748px", #out.length="520.75px",
  dpi=300, #fig.path='Figs/',
  cache=F#, echo=F, warning=F, message=F
  )

# devtools::install_github("dill/emoGG")
library(pacman)
p_load(
  broom, tidyverse,
  latex2exp, ggplot2, ggthemes, ggforce, viridis, extrafont, gridExtra,
  kableExtra, snakecase, janitor,
  data.table, dplyr, estimatr,
  lubridate, knitr, parallel,
  lfe,
  here, magrittr
)
# Define pink color
red_pink <- "#e64173"
turquoise <- "#20B2AA"
orange <- "#FFA500"
red <- "#fb6107"
blue <- "#2b59c3"
green <- "#8bb174"
grey_light <- "grey70"
grey_mid <- "grey50"
grey_dark <- "grey20"
purple <- "#6A5ACD"
slate <- "#314f4f"
# Dark slate grey: #314f4f
# Knitr options
opts_chunk$set(
  comment = "#>",
  fig.align = "center",
  fig.height = 7,
  fig.width = 10.5,
  warning = F,
  message = F
)
opts_chunk$set(dev = "svg")
options(device = function(file, width, height) {
  svg(tempfile(), width = width, height = height)
})
options(crayon.enabled = F)
options(knitr.table.format = "html")
# A blank theme for ggplot
theme_empty <- theme_bw() + theme(
  line = element_blank(),
  rect = element_blank(),
  strip.text = element_blank(),
  axis.text = element_blank(),
  plot.title = element_blank(),
  axis.title = element_blank(),
  plot.margin = structure(c(0, 0, -0.5, -1), unit = "lines", valid.unit = 3L, class = "unit"),
  legend.position = "none"
)
theme_simple <- theme_bw() + theme(
  line = element_blank(),
  panel.grid = element_blank(),
  rect = element_blank(),
  strip.text = element_blank(),
  axis.text.x = element_text(size = 18, family = "STIXGeneral"),
  axis.text.y = element_blank(),
  axis.ticks = element_blank(),
  plot.title = element_blank(),
  axis.title = element_blank(),
  # plot.margin = structure(c(0, 0, -1, -1), unit = "lines", valid.unit = 3L, class = "unit"),
  legend.position = "none"
)
theme_axes_math <- theme_void() + theme(
  text = element_text(family = "MathJax_Math"),
  axis.title = element_text(size = 22),
  axis.title.x = element_text(hjust = .95, margin = margin(0.15, 0, 0, 0, unit = "lines")),
  axis.title.y = element_text(vjust = .95, margin = margin(0, 0.15, 0, 0, unit = "lines")),
  axis.line = element_line(
    color = "grey70",
    size = 0.25,
    arrow = arrow(angle = 30, length = unit(0.15, "inches")
  )),
  plot.margin = structure(c(1, 0, 1, 0), unit = "lines", valid.unit = 3L, class = "unit"),
  legend.position = "none"
)
theme_axes_serif <- theme_void() + theme(
  text = element_text(family = "MathJax_Main"),
  axis.title = element_text(size = 22),
  axis.title.x = element_text(hjust = .95, margin = margin(0.15, 0, 0, 0, unit = "lines")),
  axis.title.y = element_text(vjust = .95, margin = margin(0, 0.15, 0, 0, unit = "lines")),
  axis.line = element_line(
    color = "grey70",
    size = 0.25,
    arrow = arrow(angle = 30, length = unit(0.15, "inches")
  )),
  plot.margin = structure(c(1, 0, 1, 0), unit = "lines", valid.unit = 3L, class = "unit"),
  legend.position = "none"
)
theme_axes <- theme_void() + theme(
  text = element_text(family = "Fira Sans Book"),
  axis.title = element_text(size = 18),
  axis.title.x = element_text(hjust = .95, margin = margin(0.15, 0, 0, 0, unit = "lines")),
  axis.title.y = element_text(vjust = .95, margin = margin(0, 0.15, 0, 0, unit = "lines")),
  axis.line = element_line(
    color = grey_light,
    size = 0.25,
    arrow = arrow(angle = 30, length = unit(0.15, "inches")
  )),
  plot.margin = structure(c(1, 0, 1, 0), unit = "lines", valid.unit = 3L, class = "unit"),
  legend.position = "none"
)
theme_set(theme_gray(base_size = 20))
# Column names for regression results
reg_columns <- c("Term", "Est.", "S.E.", "t stat.", "p-Value")
# Function for formatting p values
format_pvi <- function(pv) {
  return(ifelse(
    pv < 0.0001,
    "<0.0001",
    round(pv, 4) %>% format(scientific = F)
  ))
}
format_pv <- function(pvs) lapply(X = pvs, FUN = format_pvi) %>% unlist()
# Tidy regression results table
tidy_table <- function(x, terms, highlight_row = 1, highlight_color = "black", highlight_bold = T, digits = c(NA, 3, 3, 2, 5), title = NULL) {
  x %>%
    tidy() %>%
    select(1:5) %>%
    mutate(
      term = terms,
      p.value = p.value %>% format_pv()
    ) %>%
    kable(
      col.names = reg_columns,
      escape = F,
      digits = digits,
      caption = title
    ) %>%
    kable_styling(font_size = 20) %>%
    row_spec(1:nrow(tidy(x)), background = "white") %>%
    row_spec(highlight_row, bold = highlight_bold, color = highlight_color)
}
```

```{css, echo = F, eval = T}
@media print {
  .has-continuation {
    display: block !important;
  }
}
remark-slide-content {
  font-size: 22px;
  padding: 20px 80px 20px 80px;
}
.remark-code, .remark-inline-code {
  background: #f0f0f0;
}
.remark-code {
  font-size: 16px;
}
.mid. remark-code { /*Change made here*/
  font-size: 60% !important;
}
.tiny .remark-code { /*Change made here*/
  font-size: 40% !important;
}
```

```{r library, warning=F, echo=F, message=F, eval=TRUE}


library(tidyverse)  # data manipulation and visualization
library(gridExtra)  # plot arrangement
library(patchwork)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(tidyr)
library(janitor)
library(httr)
library(tidytext)
library(kableExtra)
library(data.table)


```

```{r importDta, warning=F, echo=F, message=F, eval=TRUE}

xiaomiD <- read.csv2("../Dta/09.07-16.07allcsv.csv") %>%
  select(X.3) %>%
  row_to_names(.,1) %>%
  mutate(Published = substr(Published,1,10)) #%>%
#mutate(Datum = as.Date(Published,"d%.m%.Y%"))

Datum  <- mutate(xiaomiD, b2= as.Date(Published, format= "%d.%m.%Y")) %>%
  select(-Published) %>%
  rename(Datum =b2)


xiaomi <- readxl::read_excel("../Dta/09.07-16.07all.xlsx") %>% 
  row_to_names(.,1) %>% 
  clean_names() %>%
#  select(-c(1,17:25,28:33,37:41)) %>%
  select(-published,-indexed,-category,-image,-languages) %>%
  cbind.data.frame(Datum)

```

```{r lexicon, echo=FALSE, message=FALSE, warning=FALSE}
## M-Files ----

# function to parse JSON from http conenctiion
parseJSON <- function(x) {
  xCon <- content(x, as = "text", type = "aplication/json", encoding = "UTF-8")
  xCon <- jsonlite::fromJSON(xCon, flatten = TRUE)
  xCon
}

# GET REST API function M-Files
mfiles_get <- function(token, resource){
  req <- GET(url = paste0('http://server.contentio.biz/REST', resource),
             add_headers('X-Authentication' = token, 'content-type' = "application/json"))
  result <- parseJSON(req)
  return(result)
}

# GET token M-Files
req <- POST(url = 'http://server.contentio.biz/REST/server/authenticationtokens.aspx', 
            config = add_headers('content-type' = "application/json"),
            body = list(Username = "msagovac", Password = "Wc8O10TaHz40",
                        VaultGuid = "{7145BCEB-8FE2-4278-AD3B-7AE70374FF8A}",
                        ComputerName  = "CT-VM-01"),
            encode = "json", verbose())
token <- parseJSON(req)[[1]]

# M-FILES DOWNLOAD FILES
mfiles_downlaod <- function(objType, objId, fileId) {
  req <- GET(url = paste0('http://server.contentio.biz/REST/objects/', objType, '/', 
                          objId, '/latest/files/',fileId , '/content'),
             add_headers('X-Authentication' = token))
  reqCon <- content(req, as = "text", encoding = "UTF-8")
  if (is.na(reqCon)) {
    reqCon <- content(req, as = "raw", encoding = "UTF-8")
    reqCon <- rawToChar(reqCon, multiple = FALSE)
    reqCon <- iconv(reqCon, "", "UTF-8")
  }
  reqCon
}
mfiles_downlaod_txt <- function(objType, objId, fileId, ext = ".csv") {
  req <- GET(url = paste0('http://server.contentio.biz/REST/objects/', objType, '/', 
                          objId, '/latest/files/',fileId , '/content'),
             add_headers('X-Authentication' = token))
  reqCon <- httr::content(req)
  tempFileSave <- paste0(tempfile(), ext)
  writeBin(reqCon, tempFileSave)
  return(tempFileSave)
}


# GET classess, props and others
prop <- mfiles_get(token, "/structure/properties")
prop <- prop %>% 
  select(DataType, ID, Name, ObjectType) %>% 
  dplyr::arrange(Name)
objs <- mfiles_get(token, "/structure/objecttypes")
mfilesClass <- mfiles_get(token, "/structure/classes")

CroSentilex_n <- read.delim(mfiles_downlaod_txt("0", 136679, 136711, ext = ".txt"),
                            header = FALSE,
                            sep = " ",
                            stringsAsFactors = FALSE) %>% 
  rename(word = "V1", sentiment = "V2" ) %>%
  mutate(brija = "NEG")

CroSentilex_p <- read.delim(mfiles_downlaod_txt("0", 136681, 136713, ext = ".txt"),
                            header = FALSE,
                            sep = " ",
                            stringsAsFactors = FALSE) %>% 
  rename(word = "V1", sentiment = "V2" ) %>%
  mutate(brija = "POZ")
Crosentilex_sve <- rbind(setDT(CroSentilex_n), setDT(CroSentilex_p))
#head(Crosentilex_sve)

CroSentilex_Gold  <- read.delim2(mfiles_downlaod_txt("0", 136680, 136712, ext = ".txt"),
                                 header = FALSE,
                                 sep = " ",
                                 stringsAsFactors = FALSE) %>%
  rename(word = "V1", sentiment = "V2" ) 

CroSentilex_Gold[1,1] <- "dati"
CroSentilex_Gold$sentiment <- str_replace(CroSentilex_Gold$sentiment , "-", "1")
CroSentilex_Gold$sentiment <- str_replace(CroSentilex_Gold$sentiment , "\\+", "2")
CroSentilex_Gold$sentiment <- as.numeric(unlist(CroSentilex_Gold$sentiment))
#head(CroSentilex_Gold)

# leksikoni
stopwords_cro <- get_stopwords(language = "hr", source = "stopwords-iso")
my_stop_words <- tibble(
  word = c(
    "jedan",
    "e","prvi", "dva","dvije","drugi",
    "tri","tre?i","pet","kod",
    "ove","ova",  "ovo","bez",
    "evo","oko",  "om", "ek",
    "mil","tko","?est", "sedam",
    "osam",   "?im", "zbog",
    "prema", "dok","zato", "koji", 
    "im", "?ak","me?u", "tek",
    "koliko", "tko","kod","poput", 
    "ba?", "dakle", "osim", "svih", 
    "svoju", "odnosno", "gdje",
    "kojoj", "ovi", "toga","ima","treba","sad","to","kad", "?e","ovaj","?ta","onda","ce","ko"
  ),
  lexicon = "lux"
)
stop_corpus <- my_stop_words %>%
  bind_rows(stopwords_cro)

```

```{r tokenize, echo=FALSE, message=FALSE, warning=FALSE}

xiaomi %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_corpus, by = "word") %>%
  mutate(word = gsub("\\d+", NA, word)) %>%
  mutate(word = gsub("^[a-zA-Z]$", NA, word)) %>%
  filter(!is.na(word)) -> rijeci_clean

```



# Contents

<br>
<br>
<br>


1. [General Overview](#gen)

2. [Facebook](#fb)

3. [Forums](#for)

4. [Portals](#port)

5. [Twitter](#tw)

6. [Youtube](#yt)

7. [Press](#pres)

8. [TV](#tv)


---
class: inverse, center, middle
name: gen

# GENERAL OVERVIEW

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Trends in the complete social media space)

---

# Frequency of mention
<br>

```{r freqOFmention, echo=FALSE, message=FALSE, warning=FALSE}


rijeci_clean %>%
  filter(word %in% c("xiaomi","samsung","vivo","huawei")) %>%
  group_by(word) %>%
  count() %>%
  arrange(desc(n))-> freqOFmention

freqOFmention %>%
  rename (Word = word,
          'Number of mentions' = n) %>%
  kable() %>%
    kable_styling()
  

```
 
 
<br>
<br>
.footnote[[*]Number of mentions in the whole text corpora.]
---

# Frequency of publication
<br>
<br>

```{r freqOFpublication, echo=FALSE, message=FALSE, warning=FALSE}

rijeci_clean %>%
  filter(word %in% c("xiaomi","samsung","vivo","huawei")) %>%
  group_by(word) %>%
  summarise(n = n_distinct(id)) %>%
  arrange(desc(n)) -> freqOFpublication


freqOFpublication %>%
  rename (Word = word,
          'Number of publications' = n) %>%
  kable() %>%
    kable_styling()

```


.footnote[[*]Number of publications that mention the word in the whole text corpora.]

---

# Most important words

```{r words, echo=FALSE, message=FALSE, warning=FALSE}

rijeci_clean %>%
  group_by(word) %>%
  count() %>%
  arrange(desc(n)) %>% 
  ungroup() -> allWords


allWords %>%
  kable() %>%
    kable_styling() %>%
    scroll_box(width = "500px", height = "400px")
```

.footnote[[*]Words in the whole text corpora.]

---

# Most important words over time



---

# Media landscape frequency


```{r landscapeFreq, echo=FALSE, message=FALSE, warning=FALSE}

xiaomi %>% 
  group_by(source) %>%
  summarise(n = n_distinct(id)) %>%
  arrange(desc(n)) -> landscapeFreq
  

landscapeFreq %>%
  rename (Source = source,
          'Number of publications' = n) %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "500px", height = "400px")

```


.footnote[[*]Publications by social media.]

---

# Media landscape frequency by brand

```{r landscapeFreqBrand, echo=FALSE, message=FALSE, warning=FALSE, fig.height = 5, fig.width = 8}

rijeci_clean %>%
  filter(word %in% c("xiaomi","samsung","vivo","huawei")) %>%
  group_by(source, word) %>%
  summarise(n = n_distinct(id)) %>%
  arrange(desc(n)) %>%
  filter(n > 2) -> landscapeFreqBrand
  


landscapeFreqBrand %>%
  ggplot(., aes(x = reorder(source,n), y = n)) +
  geom_bar(stat = "identity", alpha = 1) +
  ylab("Number of publications") +
  xlab("Source") +
  ggtitle("Media landscape by brand")+
#  theme_bw() +
  theme(axis.text.x=element_text(angle=60,hjust=1))+
  facet_wrap(~word, scales = "free") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black"))


```



---

class: inverse, center, middle
name: fb

# FACEBOOK

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Trends on the biggest Croatian social network)

---


# Most important publications
<br>
<br>


- add size of the channels

---

# Most important authors
<br>
<br>


---

class: inverse, center, middle
name: for

# FORUMS

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Very important media for mobile phone market in Croatia)

---


# Most important forums
<br>
<br>


- add size of the channels

---

# Activity description
<br>
<br>


---

# Most importan authors
<br>
<br>

---

class: inverse, center, middle
name: port

# PORTALS

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Usualy the original content to be shared across social media)

---


# Most important portals
<br>
<br>


- add size of the channels

---

# Number of publications 
<br>
<br>


---

# Content analysis

---

class: inverse, center, middle
name: tw

# TWITTER

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Informed minority in Croatia)

---


# Most important authors
<br>
<br>


- add size of the channels

---

# Authors by the audience size
<br>
<br>


---
# Number of publications
<br>
<br>


---

class: inverse, center, middle
name: yt

# YOUTUBE

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(People that wants to know details)

---

# Videos by type
<br>
<br>


---

# Most important videos 
<br>
<br>

- analyse impressons


---

# Most important authors
<br>
<br>



---

class: inverse, center, middle
name: pres

# PRESS

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Not very important)

---


# Most important sources
<br>
<br>


---

class: inverse, center, middle
name: tv

# TV

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Very rare)

---


# Most important sources
<br>
<br>

---

# CONTACT
<br>
<br>
### Contentio d.o.o
<br>
Adress:
<br>
Phone:
<br>
Mail:
<br>
Web:



































<br>
<br>







