---
title: "SHARE OF VOICE REPORT"
author: "Croatian social media overview for September, 2021"
date: "Contentio d.o.o"
# subtitle: "<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>"
subtitle: "Xiaomi"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts] 
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(knitr)
opts_chunk$set(
  fig.align="center", #fig.width=6, fig.height=4.5, 
  # out.width="748px", #out.length="520.75px",
  dpi=400, #fig.path='Figs/',
  cache=F#, echo=F, warning=F, message=F
  )


# Define pink color
red_pink <- "#e64173"
turquoise <- "#20B2AA"
orange <- "#FFA500"
red <- "#fb6107"
blue <- "#2b59c3"
green <- "#8bb174"
grey_light <- "grey70"
grey_mid <- "grey50"
grey_dark <- "grey20"
purple <- "#6A5ACD"
slate <- "#314f4f"
# Dark slate grey: #314f4f
# Knitr options

```

```{css, echo = F, eval = T}
@media print {
  .has-continuation {
    display: block !important;
  }
}
remark-slide-content {
  font-size: 22px;
  padding: 20px 80px 20px 80px;
}
.remark-code, .remark-inline-code {
  background: #f0f0f0;
}
.remark-code {
  font-size: 16px;
}
.mid. remark-code { /*Change made here*/
  font-size: 60% !important;
}
.tiny .remark-code { /*Change made here*/
  font-size: 40% !important;
}
```

```{r library, warning=F, echo=F, message=F, eval=TRUE}


library(tidyverse)  # data manipulation and visualization
library(gridExtra)  # plot arrangement
library(patchwork)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(tidyr)
library(janitor)
library(httr)
library(tidytext)
library(kableExtra)
library(data.table)
library(scales)
library(readxl)


```





# Contents

<br>
<br>


1. [Facebook](#fb)

---

class: inverse, center, middle
name: fb

# FACEBOOK

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

()

---

```{r importFacebook, echo=FALSE, message=FALSE, warning=FALSE}



site_data_columns <- read_excel("../dta/09-21.xlsx",
                               sheet = "Facebook")

site_data_column_names <- colnames(site_data_columns)
column_data_types <- c()
for(i in 1 : length(site_data_column_names)){  

    #where date is a column name
    if(site_data_column_names[i] == "date"){
         column_data_types[i] <- "date"

         #where result is a column name
         } else if (site_data_column_names[i] == "result") {
                      column_data_types[i] <- "numeric"

         } else{
                column_data_types[i] <- "text"
        }
}
column_data_types[5] <- "date"



facebook <- readxl::read_excel("../dta/09-21.xlsx",
                               sheet = "Facebook",
                               col_types = column_data_types) %>% 
  row_to_names(.,1) %>% 
  clean_names() %>%
  select(-indexed,-category,-image,-languages) %>%
  rename(Date = na)



```


# Overview of activity
<br>
<br>

```{r generalStat,  echo=FALSE, message=FALSE, warning=FALSE}

options(digits = 2, scipen = 999, big.mark = ".")

facebook %>%
  mutate(impressions = as.numeric(impressions),
         comments = as.numeric(comments),
         engagements = as.numeric(engagements),
         likes = as.numeric(likes),
         audience = as.numeric(audience)) %>%
  rename(Activity = type) -> fbDta

fbDta %>%
  group_by(Activity) %>%
  summarise(Publications = n(),
            Impressions = sum(impressions, na.rm = TRUE),
            Comments = sum(comments, na.rm = TRUE),
            Engagements = sum(engagements, na.rm = TRUE),
            Likes = sum(likes, na.rm = TRUE)) %>%
  arrange(desc(Publications)) -> fbStat


fbStat %>%
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling()

```

.footnote[[*]Possibly interesting to see by brand.]


---

# Most important activity (impressions)
<br>
<br>

```{r,  echo=FALSE, message=FALSE, warning=FALSE}

fbDta %>%
  top_n(.,10, wt = "impressions") %>% 
  arrange(desc(impressions)) %>%
  filter(impressions > 500) %>%
  select(text, Activity, author, url, impressions, engagements, likes, Date) %>%
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
    scroll_box(width = "750px", height = "400px")

```

---

# Most important activity (engagement)
<br>
<br>

```{r,  echo=FALSE, message=FALSE, warning=FALSE}

fbDta %>%
  top_n(.,10, wt = "engagements") %>% 
  arrange(desc(engagements)) %>%
  filter(engagements > 500) %>%
  select(text, Activity, author, url, impressions, engagements, likes, Date) %>%
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
    scroll_box(width = "750px", height = "400px")

```

---

# Most important activity (likes)
<br>
<br>


```{r,  echo=FALSE, message=FALSE, warning=FALSE}

fbDta %>%
  top_n(.,10, wt = "likes") %>% 
  arrange(desc(likes)) %>%
  filter(likes > 50) %>%
  select(text, Activity, author, url, impressions, engagements, likes, Date) %>%
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
    scroll_box(width = "750px", height = "400px")

```

---

# Most important authors (impressions)
<br>
<br>

```{r,  echo=FALSE, message=FALSE, warning=FALSE}

fbDta %>%
  group_by(author) %>%
  top_n(.,5, wt = "impressions") %>% 
  arrange(desc(impressions)) %>%
  filter(impressions > 500) %>%
  select(author, impressions, engagements, likes, text, Activity,  url, Date) %>%
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
    scroll_box(width = "750px", height = "400px")
```

---

# Most important authors (engagement)
<br>
<br>

```{r,  echo=FALSE, message=FALSE, warning=FALSE}

fbDta %>%
  group_by(author) %>%
  top_n(.,5, wt = "engagements") %>% 
  arrange(desc(engagements)) %>%
  filter(engagements > 300) %>%
  select(author, engagements, impressions, likes, text, Activity,  url, Date) %>%
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
    scroll_box(width = "750px", height = "400px")
```


---

# Most important authors (likes)
<br>
<br>

```{r,  echo=FALSE, message=FALSE, warning=FALSE}

fbDta %>%
  group_by(author) %>%
  top_n(.,5, wt = "likes") %>% 
  arrange(desc(likes)) %>%
  filter(likes > 50) %>%
  select(author, likes, impressions, engagements, text, Activity,  url, Date) %>%
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
    scroll_box(width = "750px", height = "400px")
```


---

# Most important authors (audience) 
<br>
<br>


```{r,  echo=FALSE, message=FALSE, warning=FALSE}

fbDta %>%
  distinct(author, .keep_all = TRUE) %>%
  arrange(desc(audience)) %>%
  slice(1:50) %>%
  select( author, audience,profile) %>%
  arrange(desc(audience)) %>% 
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
    scroll_box(width = "750px", height = "400px")

#fbDta %>%
#  group_by(author) %>%
#  count() %>%
#  arrange(desc(n))

```


---

# CONTACT






























































