---
title: "SHARE OF VOICE REPORT"
author: "Croatian social media overview for August, 2021"
date: "Contentio d.o.o"
# subtitle: "<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>"
subtitle: "Xiaomi"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts] 
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(knitr)
opts_chunk$set(
  fig.align="center", #fig.width=6, fig.height=4.5, 
  # out.width="748px", #out.length="520.75px",
  dpi=400, #fig.path='Figs/',
  cache=F#, echo=F, warning=F, message=F
  )


# Define pink color
red_pink <- "#e64173"
turquoise <- "#20B2AA"
orange <- "#FFA500"
red <- "#fb6107"
blue <- "#2b59c3"
green <- "#8bb174"
grey_light <- "grey70"
grey_mid <- "grey50"
grey_dark <- "grey20"
purple <- "#6A5ACD"
slate <- "#314f4f"
# Dark slate grey: #314f4f
# Knitr options

```

```{css, echo = F, eval = T}
@media print {
  .has-continuation {
    display: block !important;
  }
}
remark-slide-content {
  font-size: 22px;
  padding: 20px 80px 20px 80px;
}
.remark-code, .remark-inline-code {
  background: #f0f0f0;
}
.remark-code {
  font-size: 16px;
}
.mid. remark-code { /*Change made here*/
  font-size: 60% !important;
}
.tiny .remark-code { /*Change made here*/
  font-size: 40% !important;
}
```

```{r library, warning=F, echo=F, message=F, eval=TRUE}


library(tidyverse)  # data manipulation and visualization
library(gridExtra)  # plot arrangement
library(patchwork)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(tidyr)
library(janitor)
library(httr)
library(tidytext)
library(kableExtra)
library(data.table)
library(scales)
library(readxl)


```


```{r importImprove, warning=F, echo=F, message=F, eval=FALSE}

path <- "../Dta/Xiaomi full.xlsx"


data <- lapply(excel_sheets(path),
              read_xlsx,
              path = path,
              skip = 1,
              .name_repair = "tolower")

all <- data[[1]]
instagram <- data[[2]]
forums <- data[[3]]
portals <- data[[4]]
youtube <- data[[5]]
twitter <- data[[6]]
press <- data[[7]]
facebook <- data[[8]]
tv <-  data[[9]]

```



```{r importDta, warning=F, echo=F, message=F, eval=TRUE}

xiaomiD <- read.csv2("../Dta/08-21.csv") %>%
  select(X.3) %>%
  row_to_names(.,1) %>%
  mutate(Published = substr(Published,1,10)) #%>%
#mutate(Datum = as.Date(Published,"d%.m%.Y%"))

Datum  <- mutate(xiaomiD, b2= as.Date(Published, format= "%d.%m.%Y")) %>%
  select(-Published) %>%
  rename(Datum =b2)


xiaomi <- readxl::read_excel("../Dta/08-21.xlsx") %>% 
  row_to_names(.,1) %>% 
  clean_names() %>%
#  select(-c(1,17:25,28:33,37:41)) %>%
  select(-published,-indexed,-category,-image,-languages) %>%
  cbind.data.frame(Datum)

```

```{r lexicon, echo=FALSE, message=FALSE, warning=FALSE}
## M-Files ----

# function to parse JSON from http conenctiion
parseJSON <- function(x) {
  xCon <- content(x, as = "text", type = "aplication/json", encoding = "UTF-8")
  xCon <- jsonlite::fromJSON(xCon, flatten = TRUE)
  xCon
}

# GET REST API function M-Files
mfiles_get <- function(token, resource){
  req <- GET(url = paste0('http://server.contentio.biz/REST', resource),
             add_headers('X-Authentication' = token, 'content-type' = "application/json"))
  result <- parseJSON(req)
  return(result)
}

# GET token M-Files
req <- POST(url = 'http://server.contentio.biz/REST/server/authenticationtokens.aspx', 
            config = add_headers('content-type' = "application/json"),
            body = list(Username = "msagovac", Password = "Wc8O10TaHz40",
                        VaultGuid = "{7145BCEB-8FE2-4278-AD3B-7AE70374FF8A}",
                        ComputerName  = "CT-VM-01"),
            encode = "json", verbose())
token <- parseJSON(req)[[1]]

# M-FILES DOWNLOAD FILES
mfiles_downlaod <- function(objType, objId, fileId) {
  req <- GET(url = paste0('http://server.contentio.biz/REST/objects/', objType, '/', 
                          objId, '/latest/files/',fileId , '/content'),
             add_headers('X-Authentication' = token))
  reqCon <- content(req, as = "text", encoding = "UTF-8")
  if (is.na(reqCon)) {
    reqCon <- content(req, as = "raw", encoding = "UTF-8")
    reqCon <- rawToChar(reqCon, multiple = FALSE)
    reqCon <- iconv(reqCon, "", "UTF-8")
  }
  reqCon
}
mfiles_downlaod_txt <- function(objType, objId, fileId, ext = ".csv") {
  req <- GET(url = paste0('http://server.contentio.biz/REST/objects/', objType, '/', 
                          objId, '/latest/files/',fileId , '/content'),
             add_headers('X-Authentication' = token))
  reqCon <- httr::content(req)
  tempFileSave <- paste0(tempfile(), ext)
  writeBin(reqCon, tempFileSave)
  return(tempFileSave)
}


# GET classess, props and others
prop <- mfiles_get(token, "/structure/properties")
prop <- prop %>% 
  select(DataType, ID, Name, ObjectType) %>% 
  dplyr::arrange(Name)
objs <- mfiles_get(token, "/structure/objecttypes")
mfilesClass <- mfiles_get(token, "/structure/classes")

CroSentilex_n <- read.delim(mfiles_downlaod_txt("0", 136679, 136711, ext = ".txt"),
                            header = FALSE,
                            sep = " ",
                            stringsAsFactors = FALSE) %>% 
  rename(word = "V1", sentiment = "V2" ) %>%
  mutate(brija = "NEG")

CroSentilex_p <- read.delim(mfiles_downlaod_txt("0", 136681, 136713, ext = ".txt"),
                            header = FALSE,
                            sep = " ",
                            stringsAsFactors = FALSE) %>% 
  rename(word = "V1", sentiment = "V2" ) %>%
  mutate(brija = "POZ")
Crosentilex_sve <- rbind(setDT(CroSentilex_n), setDT(CroSentilex_p))
#head(Crosentilex_sve)

CroSentilex_Gold  <- read.delim2(mfiles_downlaod_txt("0", 136680, 136712, ext = ".txt"),
                                 header = FALSE,
                                 sep = " ",
                                 stringsAsFactors = FALSE) %>%
  rename(word = "V1", sentiment = "V2" ) 

CroSentilex_Gold[1,1] <- "dati"
CroSentilex_Gold$sentiment <- str_replace(CroSentilex_Gold$sentiment , "-", "1")
CroSentilex_Gold$sentiment <- str_replace(CroSentilex_Gold$sentiment , "\\+", "2")
CroSentilex_Gold$sentiment <- as.numeric(unlist(CroSentilex_Gold$sentiment))
#head(CroSentilex_Gold)

# leksikoni
stopwords_cro <- get_stopwords(language = "hr", source = "stopwords-iso")
my_stop_words <- tibble(
  word = c(
    "jedan",
    "e","prvi", "dva","dvije","drugi",
    "tri","tre?i","pet","kod",
    "ove","ova",  "ovo","bez",
    "evo","oko",  "om", "ek",
    "mil","tko","?est", "sedam",
    "osam",   "?im", "zbog",
    "prema", "dok","zato", "koji", 
    "im", "?ak","me?u", "tek",
    "koliko", "tko","kod","poput", 
    "ba?", "dakle", "osim", "svih", 
    "svoju", "odnosno", "gdje",
    "kojoj", "ovi", "toga","ima","treba","sad","to","kad", "?e","ovaj","?ta","onda","ce","ko"
  ),
  lexicon = "lux"
)
stop_corpus <- my_stop_words %>%
  bind_rows(stopwords_cro)

```

```{r tokenize, echo=FALSE, message=FALSE, warning=FALSE}

xiaomi %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_corpus, by = "word") %>%
  mutate(word = gsub("\\d+", NA, word)) %>%
  mutate(word = gsub("^[a-zA-Z]$", NA, word)) %>%
  filter(!is.na(word)) -> rijeci_clean

```


# Contents

<br>
<br>

1. [General Overview](#gen)

2. [Facebook](#fb)

3. [Forums](#for)

4. [Portals](#port)

5. [Twitter](#tw)

6. [Youtube](#yt)

7. [Press](#pres)

8. [Instagram](#insta)


---
class: inverse, center, middle
name: gen

# GENERAL OVERVIEW

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Trends in the Croatian social media space for mobile brands.)

---




# About
<br>
- This report covers complete Croatian social media space for August, 2021.
<br>
<br>
- Every mention of brands: xiaomi, samsung, huawei, vivo is included in the analysis.
<br>
<br>
- The general overview part covers the full media space.
<br>
<br>
- The other parts cover individual social media.

---

# Findings
<br>
- Most social media activity is on forums and Facebook.
<br>
<br>
- Small number of newspaper (portal) articles are important and shared across different social media.
<br>
<br>
- Recommended influencers are on forums and facebook.


---


# Frequency of mention
<br>
<br>
<br>
```{r freqOFmention, echo=FALSE, message=FALSE, warning=FALSE}


rijeci_clean %>%
  filter(word %in% c("xiaomi","samsung","vivo","huawei")) %>%
  group_by(word) %>%
  count() %>%
  arrange(desc(n))-> freqOFmention

freqOFmention %>%
  rename (Brand = word,
          'Number of mentions' = n) %>%
  kable() %>%
    kable_styling()

#freqOFmention %>%
#  ggplot(.,aes(word, n)) + geom_bar(stat= "identity")
  

```
 
 
<br>
<br>
.footnote[[*]Number of brand mentions in the whole text corpora.]
---

# Frequency of publication
<br>
<br>
<br>
```{r freqOFpublication, echo=FALSE, message=FALSE, warning=FALSE}

rijeci_clean %>%
  filter(word %in% c("xiaomi","samsung","vivo","huawei")) %>%
  group_by(word) %>%
  summarise(n = n_distinct(id)) %>%
  arrange(desc(n)) -> freqOFpublication


freqOFpublication %>%
  rename (Brand = word,
          'Number of publications' = n) %>%
  kable() %>%
    kable_styling()

```


.footnote[[*]Number of distinct publications that mention the brand.]

---

# Most important words
<br>
```{r words, echo=FALSE, message=FALSE, warning=FALSE}

rijeci_clean %>%
  group_by(word) %>%
  count() %>%
  arrange(desc(n)) %>% 
  ungroup() %>%
  rename("Word" = word, "No. of occurences" = n)-> allWords


allWords %>%
  kable() %>%
    kable_styling() %>%
    scroll_box(width = "700px", height = "400px")
```

.footnote[[*]Words in the whole text corpora.]

---

# Most important words over time

```{r brandOverTime, echo=FALSE, message=FALSE, warning=FALSE, fig.height = 3, fig.width = 5}

brands <- c("xiaomi", "samsung", "huawei", "vivo")

rijeci_clean %>%
#  mutate(Datum = lubridate::floor_date(Datum, "week")) %>% 
  group_by(Datum) %>%
  count(word) %>% 
  mutate(gn = sum(n)) %>% 
  filter(word %in% brands) %>%
  ggplot(., aes(Datum, n / gn)) + 
#  geom_bar(stat = "identity") +
  geom_line() + 
  ggtitle("Brand mentions over time") +
  ylab("% in the corpus") +
  xlab("Date") +
  facet_wrap(~ word, scales = "free_y") +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_x_date(labels = date_format("%d-%m")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black"))


```

.footnote[[*]Percentage (%) of words (brands) in the full text corpora on a given day.]


---

# Media landscape frequency
<br>

```{r landscapeFreq, echo=FALSE, message=FALSE, warning=FALSE}

xiaomi %>% 
  group_by(source) %>%
  summarise(n = n_distinct(id)) %>%
  arrange(desc(n)) -> landscapeFreq
  

landscapeFreq %>%
  rename (Source = source,
          'Number of publications' = n) %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "500px", height = "400px")

```


.footnote[[*]Uniqe publications that mention one or more brands per social media.]

---

# Media landscape frequency by brand
<br>

```{r landscapeFreqBrand, echo=FALSE, message=FALSE, warning=FALSE, fig.height = 5, fig.width=12}

rijeci_clean %>%
  filter(word %in% c("xiaomi","samsung","vivo","huawei")) %>%
  group_by(source, word) %>%
  summarise(n = n_distinct(id)) %>%
  arrange(desc(n)) %>%
  filter(n > 2) -> landscapeFreqBrand
  


landscapeFreqBrand %>%
  ggplot(., aes(x = reorder(source,n), y = n)) +
  geom_bar(stat = "identity", alpha = 1) +
  facet_wrap(~word, scales = "free") +
  ylab("Number of publications") +
  xlab("Source") +
  ggtitle("Media landscape by brand") +
#  theme_bw() +
#  theme(axis.text.x=element_text(angle=45,hjust=1)) 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.text.x=element_text(angle=35,hjust=1))


```


.footnote[[*]Number of publications by the brand and social media.]

---

class: inverse, center, middle
name: fb

# FACEBOOK

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Most active social media for mobile phones.)

---

```{r importFacebook, echo=FALSE, message=FALSE, warning=FALSE}

site_data_columns <- read_excel("../Dta/08-21.xlsx",
                               sheet = "Facebook")

site_data_column_names <- colnames(site_data_columns)
column_data_types <- c()
for(i in 1 : length(site_data_column_names)){  

    #where date is a column name
    if(site_data_column_names[i] == "date"){
         column_data_types[i] <- "date"

         #where result is a column name
         } else if (site_data_column_names[i] == "result") {
                      column_data_types[i] <- "numeric"

         } else{
                column_data_types[i] <- "text"
        }
}
column_data_types[5] <- "date"



facebook <- readxl::read_excel("../Dta/08-21.xlsx",
                               sheet = "Facebook",
                               col_types = column_data_types) %>% 
  row_to_names(.,1) %>% 
  clean_names() %>%
  select(-indexed,-category,-image,-languages) %>%
  rename(Date = na)



```


# Overview of activity
<br>
<br>

```{r generalStat,  echo=FALSE, message=FALSE, warning=FALSE}

options(digits = 2, scipen = 999, big.mark = ".")

facebook %>%
  mutate(impressions = as.numeric(impressions),
         comments = as.numeric(comments),
         engagements = as.numeric(engagements),
         likes = as.numeric(likes),
         audience = as.numeric(audience)) %>%
  rename(Activity = type) -> fbDta

fbDta %>%
  group_by(Activity) %>%
  summarise(Publications = n(),
            Impressions = sum(impressions, na.rm = TRUE),
            Comments = sum(comments, na.rm = TRUE),
            Engagements = sum(engagements, na.rm = TRUE),
            Likes = sum(likes, na.rm = TRUE)) %>%
  arrange(desc(Publications)) -> fbStat


fbStat %>%
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling()

```

.footnote[[*]Possibly interesting to see by brand.]


---

# Most important activity (impressions)
<br>
<br>

```{r,  echo=FALSE, message=FALSE, warning=FALSE}

fbDta %>%
  top_n(.,10, wt = "impressions") %>% 
  arrange(desc(impressions)) %>%
  select(text, Activity, author, url, impressions, engagements, likes, Date) %>%
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
    scroll_box(width = "750px", height = "400px")

```

---

# Most important activity (engagement)
<br>
<br>

```{r,  echo=FALSE, message=FALSE, warning=FALSE}

fbDta %>%
  top_n(.,10, wt = "engagements") %>% 
  arrange(desc(engagements)) %>%
  select(text, Activity, author, url, impressions, engagements, likes, Date) %>%
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
    scroll_box(width = "750px", height = "400px")

```

---

# Most important activity (likes)
<br>
<br>


```{r,  echo=FALSE, message=FALSE, warning=FALSE}

fbDta %>%
  top_n(.,10, wt = "likes") %>% 
  arrange(desc(likes)) %>%
  select(text, Activity, author, url, impressions, engagements, likes, Date) %>%
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
    scroll_box(width = "750px", height = "400px")

```

---

# Most important authors (impressions)
<br>
<br>

```{r,  echo=FALSE, message=FALSE, warning=FALSE}

fbDta %>%
  group_by(author) %>%
  top_n(.,5, wt = "impressions") %>% 
  arrange(desc(impressions)) %>%
  select(author, impressions, engagements, likes, text, Activity,  url, Date) %>%
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
    scroll_box(width = "750px", height = "400px")
```

---

# Most important authors (engagement)
<br>
<br>

```{r,  echo=FALSE, message=FALSE, warning=FALSE}

fbDta %>%
  group_by(author) %>%
  top_n(.,5, wt = "engagements") %>% 
  arrange(desc(engagements)) %>%
  select(author, engagements, impressions, likes, text, Activity,  url, Date) %>%
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
    scroll_box(width = "750px", height = "400px")
```


---

# Most important authors (likes)
<br>
<br>

```{r,  echo=FALSE, message=FALSE, warning=FALSE}

fbDta %>%
  group_by(author) %>%
  top_n(.,5, wt = "likes") %>% 
  arrange(desc(likes)) %>%
  select(author, likes, impressions, engagements, text, Activity,  url, Date) %>%
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
    scroll_box(width = "750px", height = "400px")
```


---

# Most important authors (audience) 
<br>
<br>


```{r,  echo=FALSE, message=FALSE, warning=FALSE}

fbDta %>%
  distinct(author, .keep_all = TRUE) %>%
  arrange(desc(audience)) %>%
  slice(1:20) %>%
  select( author, audience,profile) %>%
  arrange(desc(audience)) %>% 
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
    scroll_box(width = "750px", height = "400px")

#fbDta %>%
#  group_by(author) %>%
#  count() %>%
#  arrange(desc(n))

```

---

class: inverse, center, middle
name: for

# FORUMS

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Important media for mobile phone market in Croatia.)

---


```{r importForums, echo=FALSE, message=FALSE, warning=FALSE}

site_data_columns <- read_excel("../Dta/08-21.xlsx",
                               sheet = "Forums")

site_data_column_names <- colnames(site_data_columns)
column_data_types <- c()
for(i in 1 : length(site_data_column_names)){  

    #where date is a column name
    if(site_data_column_names[i] == "date"){
         column_data_types[i] <- "date"

         #where result is a column name
         } else if (site_data_column_names[i] == "result") {
                      column_data_types[i] <- "numeric"

         } else{
                column_data_types[i] <- "text"
        }
}
column_data_types[5] <- "date"
column_data_types[10] <- "guess"



forums <- readxl::read_excel("../Dta/08-21.xlsx",
                               sheet = "Forums",
                               col_types = column_data_types) %>% 
  row_to_names(.,1) %>% 
  clean_names() %>%
  select(title,text,"Date" = na,source,url, type, impressions, engagements, author) %>%
  mutate(impressions = as.numeric(impressions)) %>%
  mutate(engagements = as.numeric(engagements))


```

# Most important forums (activity)
<br>

```{r , echo=FALSE, message=FALSE, warning=FALSE}

forums %>%
  group_by(source) %>%
  count() %>%
  arrange(desc(n)) %>%
  rename("Forum" = source, "No. of occurences" = n)  %>% 
  kable() %>%
    kable_styling() #%>%
 #   scroll_box(width = "900px", height = "400px")

```

.footnote[[*]Occurences denote the activity on a forum that mentions the brand.]

---

# Most important forums (impressions)
<br>
<br>

```{r, echo=FALSE, message=FALSE, warning=FALSE}

forums %>%
  group_by(source) %>%
  summarise(Impressions = sum(impressions, na.rm = TRUE)) %>%
  arrange(desc(Impressions)) %>% 
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling()
  
  
```

---

# Most important forums (engagements)
<br>
<br>

```{r, echo=FALSE, message=FALSE, warning=FALSE}

forums %>%
  group_by(source) %>%
  summarise(Engagements = sum(engagements, na.rm = TRUE)) %>%
  arrange(desc(Engagements)) %>% 
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling()
  
  
```


---

# Most important influencers
<br>
<br>


```{r, echo=FALSE, message=FALSE, warning=FALSE}

forums %>%
  group_by(author, source) %>%
  summarise(Impressions = sum(impressions, na.rm = TRUE),
            Activity = n()) %>%
  arrange(desc(Impressions)) %>% 
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
     scroll_box(width = "700px", height = "400px")
  
  
```




---

class: inverse, center, middle
name: port

# PORTALS

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Original content shared across other social media.)

---


```{r importPortals, echo=FALSE, message=FALSE, warning=FALSE}

site_data_columns <- read_excel("../Dta/08-21.xlsx",
                               sheet = "Portals")

site_data_column_names <- colnames(site_data_columns)
column_data_types <- c()
for(i in 1 : length(site_data_column_names)){  

    #where date is a column name
    if(site_data_column_names[i] == "date"){
         column_data_types[i] <- "date"

         #where result is a column name
         } else if (site_data_column_names[i] == "result") {
                      column_data_types[i] <- "numeric"

         } else{
                column_data_types[i] <- "text"
        }
}
column_data_types[5] <- "date"
column_data_types[10] <- "guess"



portals <- readxl::read_excel("../Dta/08-21.xlsx",
                               sheet = "Portals",
                               col_types = column_data_types) %>% 
  row_to_names(.,1) %>% 
  clean_names() %>%
  select(title,text,"Date" = na,source,url, type, impressions, engagements, author) %>%
  mutate(impressions = as.numeric(impressions)) %>%
  mutate(engagements = as.numeric(engagements))


```

# Most important portals (publications)
<br>
<br>


```{r, echo=FALSE, message=FALSE, warning=FALSE}

portals %>%
  group_by(source) %>%
  count()  %>%
  arrange(desc(n)) %>%
  rename("Portal" = source,
         "No. of publications" = n) %>% 
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
     scroll_box(width = "700px", height = "400px")



```


---

# Most important portals (impressions) 
<br>
<br>


```{r, echo=FALSE, message=FALSE, warning=FALSE}

portals %>%
  group_by(source) %>%
  summarise(Impressions = sum(impressions, na.rm = TRUE)) %>%
  arrange(desc(Impressions)) %>%
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
     scroll_box(width = "700px", height = "400px")



```

---

# Most important articles (impressions) 
<br>
<br>


```{r, echo=FALSE, message=FALSE, warning=FALSE}

portals %>%
  group_by(title, url, source, Date) %>%
  summarise(Impressions = sum(impressions, na.rm = TRUE)) %>%
  arrange(desc(Impressions)) %>%
  select(title, Impressions, source,url, Date) %>%
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
     scroll_box(width = "800px", height = "400px")



```



---

class: inverse, center, middle
name: tw

# TWITTER

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Informed but small comunity in Croatia.)

---

```{r importTwitter, echo=FALSE, message=FALSE, warning=FALSE}

site_data_columns <- read_excel("../Dta/08-21.xlsx",
                               sheet = "Twitter")

site_data_column_names <- colnames(site_data_columns)
column_data_types <- c()
for(i in 1 : length(site_data_column_names)){  

    #where date is a column name
    if(site_data_column_names[i] == "date"){
         column_data_types[i] <- "date"

         #where result is a column name
         } else if (site_data_column_names[i] == "result") {
                      column_data_types[i] <- "numeric"

         } else{
                column_data_types[i] <- "text"
        }
}
column_data_types[5] <- "date"
column_data_types[10] <- "guess"



twitter <- readxl::read_excel("../Dta/08-21.xlsx",
                               sheet = "Twitter",
                               col_types = column_data_types) %>% 
  row_to_names(.,1) %>% 
  clean_names() %>%
  select(title,text,"Date" = na,source,url, type, impressions, engagements, author, audience, profile) %>%
  mutate(impressions = as.numeric(impressions)) %>%
  mutate(engagements = as.numeric(engagements)) %>%
  mutate(audience = as.numeric(audience))


```


# Summary of activity
<br>
<br>


```{r , echo=FALSE, message=FALSE, warning=FALSE}

twitter %>% 
  group_by(type) %>%
  count() %>%
  arrange(desc(n)) %>% 
  rename("Type of activity" = type, 
         "No. of occurences" = n) %>%
  kable() %>%
    kable_styling() #%>%
#     scroll_box(width = "700px", height = "400px")

```

---

# Most important authors
<br>
<br>

```{r , echo=FALSE, message=FALSE, warning=FALSE}


twitter %>%
  group_by(author) %>%
  count() %>%
  arrange(desc(n)) %>% 
  rename("Author" = author, 
         "No. of publications" = n) %>%
  kable() %>%
    kable_styling() %>%
     scroll_box(width = "750px", height = "400px")


```


---

# Most important tweets (impressions)
<br>
<br>



```{r, echo=FALSE, message=FALSE, warning=FALSE}

twitter %>%
  group_by(text, author, url) %>%
  summarise(Impressions = sum(impressions, na.rm = TRUE)) %>%
  arrange(desc(Impressions)) %>% 
  select(text, Impressions, author) %>%
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
     scroll_box(width = "750px", height = "400px")



```


---

# Most influential profiles (audience size)
<br>
<br>



```{r, echo=FALSE, message=FALSE, warning=FALSE}

twitter %>%
  group_by(author) %>%
  arrange(desc(audience)) %>%
  select(author,audience,profile) %>% 
  distinct(author, .keep_all = TRUE) %>% 
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
     scroll_box(width = "750px", height = "400px")

```



---

class: inverse, center, middle
name: yt

# YOUTUBE

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Social media with highest attention focus.)

---


```{r importYT, echo=FALSE, message=FALSE, warning=FALSE}

site_data_columns <- read_excel("../Dta/08-21.xlsx",
                               sheet = "YouTube")

site_data_column_names <- colnames(site_data_columns)
column_data_types <- c()
for(i in 1 : length(site_data_column_names)){  

    #where date is a column name
    if(site_data_column_names[i] == "date"){
         column_data_types[i] <- "date"

         #where result is a column name
         } else if (site_data_column_names[i] == "result") {
                      column_data_types[i] <- "numeric"

         } else{
                column_data_types[i] <- "text"
        }
}
column_data_types[5] <- "date"
column_data_types[10] <- "guess"



yt <- readxl::read_excel("../Dta/08-21.xlsx",
                               sheet = "YouTube",
                               col_types = column_data_types) %>% 
  row_to_names(.,1) %>% 
  clean_names() %>%
  select(title,text,"Date" = na,source,url, type, impressions, engagements, author,views, likes_2, comments) %>%
  mutate(impressions = as.numeric(impressions)) %>%
  mutate(engagements = as.numeric(engagements)) %>%
  mutate(views = as.numeric(views)) %>%
  mutate(likes = as.numeric(likes_2)) %>%
  mutate(comments = as.numeric(comments))


```


# Videos by type
<br>
<br>
<br>


```{r, echo=FALSE, message=FALSE, warning=FALSE}

yt %>%
  group_by(type) %>%
  count() %>% 
  rename("Type of activity" = type,
         "No. of occurences" = n) %>%
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() 

```


---

# Most important channels
<br>
<br>



```{r, echo=FALSE, message=FALSE, warning=FALSE}


yt %>%
  group_by(author) %>%
  summarise(Impressions = sum(impressions,na.rm = TRUE),
            Activity = n()) %>%
  arrange(desc(Activity)) %>%
  select(author, Activity, Impressions) %>%
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
     scroll_box(width = "750px", height = "400px")




```


---

# Most important videos 
<br>
<br>

```{r , echo=FALSE, message=FALSE, warning=FALSE}
yt %>%
  group_by(title,url, author) %>%
  summarise(Impressions = sum(impressions,na.rm = TRUE),
            Comments = sum(comments, na.rm = TRUE),
            Views = sum(views, na.rm = TRUE),
            Likes = sum(likes,na.rm = TRUE)) %>%
  arrange(desc(Impressions)) %>%
  select(title, Impressions, Comments, Views,Likes, url, author) %>%
   kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
     scroll_box(width = "750px", height = "400px")

```


---

class: inverse, center, middle
name: pres

# PRESS

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>

(Not very active media for mobile phones.)

---


```{r importPress, echo=FALSE, message=FALSE, warning=FALSE}

site_data_columns <- read_excel("../Dta/08-21.xlsx",
                               sheet = "Press")

site_data_column_names <- colnames(site_data_columns)
column_data_types <- c()
for(i in 1 : length(site_data_column_names)){  

    #where date is a column name
    if(site_data_column_names[i] == "date"){
         column_data_types[i] <- "date"

         #where result is a column name
         } else if (site_data_column_names[i] == "result") {
                      column_data_types[i] <- "numeric"

         } else{
                column_data_types[i] <- "text"
        }
}
column_data_types[5] <- "date"
column_data_types[10] <- "guess"



press <- readxl::read_excel("../Dta/08-21.xlsx",
                               sheet = "Press",
                               col_types = column_data_types) %>% 
  row_to_names(.,1) %>% 
  clean_names() %>%
  select(title,text,"Date" = na,source,url, type, impressions, engagements, author,views, likes, comments) %>%
  mutate(impressions = as.numeric(impressions)) %>%
  mutate(engagements = as.numeric(engagements)) %>%
  mutate(views = as.numeric(views)) %>%
  mutate(likes = as.numeric(likes)) %>%
  mutate(comments = as.numeric(comments))

```

# Most important sources
<br>
<br>


```{r , echo=FALSE, message=FALSE, warning=FALSE}


press %>%
  group_by(source) %>%
  summarise(Impressions = sum(impressions,na.rm = TRUE),
            Articles = n()) %>%
  arrange(desc(Articles)) %>%
  select(source, Articles, Impressions) %>%
   kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() # >%
  #   scroll_box(width = "750px", height = "400px")
  


```

---

# Most important articles



```{r , echo=FALSE, message=FALSE, warning=FALSE}


press %>%
  group_by(title, url,text,source) %>%
  summarise(Impressions = sum(impressions,na.rm = TRUE)) %>%
  arrange(desc(Impressions)) %>%
  select(title, Impressions, text, source, url) %>%
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
     scroll_box(width = "750px", height = "400px")
  
```



---

class: inverse, center, middle
name: insta

# INSTAGRAM

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>



---

```{r importInsta, echo=FALSE, message=FALSE, warning=FALSE}

site_data_columns <- read_excel("../Dta/08-21.xlsx",
                               sheet = "Instagram")

site_data_column_names <- colnames(site_data_columns)
column_data_types <- c()
for(i in 1 : length(site_data_column_names)){  

    #where date is a column name
    if(site_data_column_names[i] == "date"){
         column_data_types[i] <- "date"

         #where result is a column name
         } else if (site_data_column_names[i] == "result") {
                      column_data_types[i] <- "numeric"

         } else{
                column_data_types[i] <- "text"
        }
}
column_data_types[5] <- "date"
column_data_types[10] <- "guess"



insta <- readxl::read_excel("../Dta/08-21.xlsx",
                               sheet = "Instagram",
                               col_types = column_data_types) %>% 
  row_to_names(.,1) %>% 
  clean_names() %>%
  select(title,text,"Date" = na,source,url, type, impressions, engagements, author,views, likes_3, comments) %>%
  mutate(impressions = as.numeric(impressions)) %>%
  mutate(engagements = as.numeric(engagements)) %>%
  mutate(views = as.numeric(views)) %>%
  mutate(likes = as.numeric(likes_3)) %>%
  mutate(comments = as.numeric(comments))


```


# Most important posts (impressions)
<br>
<br>


```{r , echo=FALSE, message=FALSE, warning=FALSE}

insta %>%
  group_by(url,text) %>%
  summarise(Impressions = sum(impressions,na.rm = TRUE)) %>%
  arrange(desc(Impressions)) %>%
  select(url, Impressions, text) %>%
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
     scroll_box(width = "750px", height = "400px")


```

---

# Most important posts (likes)
<br>
<br>

```{r, echo=FALSE, message=FALSE, warning=FALSE}

insta %>%
  group_by(url,text) %>%
  summarise(Likes = sum(likes,na.rm = TRUE)) %>%
  arrange(desc(Likes)) %>%
  select(url, Likes, text) %>%
  kable(format.args = list(decimal.mark = ',', big.mark = ".")) %>%
    kable_styling() %>%
     scroll_box(width = "700px", height = "400px")


```


---

# CONTACT
<br>
<br>
### Contentio d.o.o
<br>
Adress: Kralja Stjepana Tomaševića 7 , 10410, Velika Gorica
<br>
Phone: + 385 98 162 30 52
<br>
Mail: luka.sikic.gm@gmail.com
<br>
Web: http://www.contentio.biz/contact/





























































